Simple Wind Models

### 2010-06-10 Winds/papers/Theory/First/wind_simple.tex
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@4994 ac11df5e-a788-c23b-a8e1-c758c323924d

\documentclass[12pt,preprint]{aastex}
\usepackage{natbib,amsmath}
\special{papersize=8.5in,11in}
\begin{document}

\newcommand{\aconfig}{a~$^6$D}
\newcommand{\zconfig}{z~$^6$D$^0$}
\newcommand{\mvr}{v_{\rm r}}
\newcommand{\naid}{\ion{Na}{1}~$\lambda\lambda 5891, 5897$}
\newcommand{\mgiid}{\ion{Mg}{2}~$\lambda\lambda 2796, 2803$}
\newcommand{\mgiia}{\ion{Mg}{2}~$\lambda 2796$}
\newcommand{\mgiib}{\ion{Mg}{2}~$\lambda 2803$}
\newcommand{\feiia}{\ion{Fe}{2}~$\lambda 2586$}
\newcommand{\feiib}{\ion{Fe}{2}~$\lambda 2600$}
\newcommand{\feiid}{\ion{Fe}{2}~$\lambda\lambda 2586, 2600$}
\newcommand{\nmg}{$n_{\rm Mg^+}$}
\newcommand{\mnmg}{n_{\rm Mg^+}}
\newcommand{\nfe}{$n_{\rm Fe^+}$}
\newcommand{\mnfe}{n_{\rm Fe^+}}
\def\hub{h_{72}^{-1}}
\def\umfp{{\hub \, \rm Mpc}}
\def\mzq{z_q}
\def\zabs{$z_{\rm abs}$}
\def\mzabs{z_{\rm abs}}
\def\intl{\int\limits}
\def\cmma{\;\;\; ,}
\def\perd{\;\;\; .}
\def\ltk{\left [ \,}
\def\ltp{\left ( \,}
\def\ltb{\left \{ \,}
\def\rtk{\, \right  ] }
\def\rtp{\, \right  ) }
\def\rtb{\, \right \} }
\def\sci#1{{\; \times \; 10^{#1}}}
\def \rAA {\rm \AA}
\def \zem {$z_{\rm em}$}
\def \mzem {z_{\rm em}}
\def\smm{\sum\limits}
\def \cmm  {cm$^{-2}$}
\def \cmmm {cm$^{-3}$}
\def \kms  {km~s$^{-1}$}
\def \mkms  {{\rm km~s^{-1}}}
\def \lyaf {Ly$\alpha$ forest}
\def \Lya  {Ly$\alpha$}
\def \lya  {Ly$\alpha$}
\def \mlya  {Ly\alpha}
\def \Lyb  {Ly$\beta$}
\def \lyb  {Ly$\beta$}
\def \lyg  {Ly$\gamma$}
\def \ly5  {Ly-5}
\def \ly6  {Ly-6}
\def \ly7  {Ly-7}
\def \nhi  {$N_{\rm HI}$}
\def \mnhi  {N_{\rm HI}}
\def \lnhi {$\log N_{HI}$}
\def \mlnhi {\log N_{HI}}
\def \etal {\textit{et al.}}
\def \lyaf {Lyman--$\alpha$ forest}
\def \mnmin {\mnhi^{\rm min}}
\def \nmin {$\mnhi^{\rm min}$}
\def \O {${\mathcal O}(N,X)$}
\newcommand{\cm}[1]{\, {\rm cm^{#1}}}
\def \snrlim {SNR$_{lim}$}

@@

\begin{abstract}
\begin{itemize}
\item Emission is a generic feature of (nearly) isotropic winds.  This
  emission fills in absorption at $v \approx 0$, significantly
  complicating the absorption-line analysis. 
\end{abstract}

@@

The Mg$^+$ ion, with a single 3s electron in the ground-state,
exhibits an alkali doublet of transitions similar to the
\lya\ transitions of neutral hydrogen.  In Figure~\ref{fig:energy}
we present the energy level diagram for this 
\mgiid\ doublet.  In non-relativistic quantum
mechanics, the 2p$^6$3p level is said to be split by spin-orbit
coupling which produces the line doublet.  These are the only
\ion{Mg}{2} electric-dipole transitions 
with wavelengths near 2800\AA. Also, the transtion connecting
the $\rm {}^2P_{3/2}$ and $\rm {}^2P_{1/2}$ states is forbidden by several
selection rules.  Therefore, an absorption from
2p$^6$^3s~$\to$~2p$^6$3p 
is followed nearly 100$\%$ of the time by a spontaneous decay to the
ground state and our treatment will ignore any other possibilities
(e.g.\ absorption of a second photon).

@@

Iron exhibits the most complex set of energy levels of the elements
frequently studied in astrophysics.  The Fe$^+$ ion alone has over XXX
energy levels recorded \citep{iron}, and even this is an
incomplete list.  
One reason for the complexity of iron is
that the majority of its configurations exhibit fine-structure splitting.
This includes the ground-state configuration (\aconfig) which is split
into 5 levels with 
excitation energies $T_{\rm ex} \equiv \Delta E / k$ ranging from
$T_{\rm{ex} \approx
500-1500$\,K.  These levels are usually labelled by the total angular momentum
$J$, with the ground-state having $J=9/2$ (Figure~\ref{fig:energy}).  
Transitions between these fine-structure levels are 
forbidden (magnetic-dipole) with spontaneous decay times of several hours.

@@

In Figure~\ref{fig:fiducial_nvt} we plot the density and velocity
profiles against radius for the fiducial wind model;  
their single power-law expressions are evident.  The figure also
shows the optical depth for the \mgiia\ transition ($\tau_{2796}$).
Although plotted against radius, we calcualted $\tau_{2796}$ by
summing the opacity as a function of velocity in discrete and small radial intervals
between $r_{\rm inner}$  and $r_{\rm outer}$.   It was then mapped
onto radius using the radial velocity profile. 
The curve agrees well with that derived using the Sobolev approximation.
We emphasize that the optical depth vs.\ velocity are the primary
factors that establish the absorption/emission profiles of the
\ion{Mg}{2} and \ion{Fe}{2} transitions.  In this respect, the 
parameters that establish the size of the wind (and source) are
essentially arbitrary.   In contrast, the adopted Doppler paramter
($b_{\rm turb} = 15 \mkms$) does have a modest impact on the optical
depth profile, especially at large optical depths.  A larger/smaller
value would imply ... [FILL IN]
In turn, this would affect the resulting emission profiles.

The $\tau_{2796}$ profile peaks at $\tau_{2796}^{\rm max} \approx 30$
at a velocity $v \approx 65 \mkms$ corresponding to $r \approx 1.3
r_{\rm inner}$.  The optical depth profiles for the \mgiib\ transition
is identicaly but scaled down by the ratio of $f\lambda$.  Similarly,
the optcial depth profiles for the \ion{Fe}{2} resonance lines are
scaled by $f \lambda$ and the \nfe/\nmg\ ratio.

Using the methodology described in $\S$~\ref{sec:method}, we
propogated photons from the source and through the outflow to an
`observer' at $r \gg r_{\rm outer}$ that views the entire wind+source
complex.  In Figure~\ref{fig:fiducial_1d}, we present the spectrum
that this observer would record with the unattenuated source spectrum
normalized to unit value.   Consider first the \ion{Mg}{2} profiles;
these show the canonical P-Cygni profiles that characterize a 
source embedded within an outflow.  Strong absorption is evident at
$v < -50 \mkms$ in both transitions and each shows emission at
positive velocities.  For this isotropic and dust-free model, the
total equivalent width of the doublet must be zero
(Table~\ref{tab:fiducial_EW}), i.e.\ every photon
absorbed escapes the system at another energy, primarily at lower
frequency.  The wind simply shuffles photons in frequency space.

Focusing on the \ion{Mg}{2} absorption profiles, one notes they have
similar and non-zero depth even though their $f\lambda$ values differ
by a factor of two.  In absorption line analysis, this is generally
the tell-tale signature of a gas that has a high optical depth (i.e.\
saturated) but only partially covers the emitting source
\citep[e.g.][]{hamman10}.  In this fiducial model, however, the wind
entirely covers the source and the observed behaviour is unrelated to
any partial covering.  Figure~\ref{fig:noemiss}, which compares the
absorption profiles as derived and in the limit where photons are not
re-emitted, shows this explicitly.   One notes that the no-emission
case has a pair of strong absorption lines that absorb all photons at
$v \approx -100 \mkms$, i.e.\ these profiles are simply $\exp(-\tau)$
with $\tau$ given by the curve in Figure~\ref{fig:fiducial_nvt}.  
The actual profile, meanwhile, has been `filled in' at $v \approx -100
\mkms$ by photons scattered and re-emitted by the wind.  An
absorption-line analysis that ignores these effects
\citep[e.g.][]{sato} would systematically underestimate the true optical
depth and falsely conclude partial covering.  [MORE?]
[Dan's analytic calculation here?]

One also notes that the emission profiles of the \mgiid\ doublet
are very similar and have comparable equivalent widths.  In fact the
flux of the \mgiib\ transition even exceeds that for \mgiia.  The
profiles are similar because the absorption is saturated.
Furthermore, the flux from \mgiib\ is greater than that for
\mgiia\ because the wind speed exceeds the velocity separation
of the doublet $|\mvr|_{\rm max} > (\Delta v)_{\rm MgII}$ such
that the \mgiib\ absorption profile absorbs the red wing of the
\mgiia\ emission profile.  The relative strengths of these emission
lines, therefore, is sensitive to both the optical depth and velocity
extent of the wind.

The bottom left panel of Figure~\ref{fig:fiducial_1d} covers the
majority of the \ion{Fe}{2} UV1 transitions.  Several of these are
shown individually in the velocity plot on the right.  The line
profiles for \feiib\ is very similar to those of the \mgiid\ doublet;
one observes strong absorption to negative velocities and strong
emission at $v > 0 \mkms$ producing the P-Cygni profile.  Splitting
the profile at $v = -50 \mkms$, we measure an equivalent width
$W_{2600}^{\rm abs} = 1.19$\AA\ in absorption and $W_{2600}^{\rm em} =
-0.84$\AA\ in emission (Table~\ref{tab:fiducial_EW}) for a total
equivalent width of $W_{2600}^{\rm TOT} \approx 0.35$\AA.  
[Point out that if $\tau_{2600}$ were higher, than the photons would
likely be more trapped and more would come out as 2626.  Also a
v=0km/s component might make quite a difference.]
In contrast, the \feiia\ resonance line shows much weaker emission and
a much higher total equivalent width ($W_{2586}^{\rm TOT} = XX$\AA).
The differences related directly to Einstein coefficients for the
transitions connecting the upper levels of \feiid\ to the 
fine-structure levels of a~$^6$D.  In the case of \feiib, the
\ion{Fe}{2}~2626 transition that returns to the a~$^6$D$_{7/2}$
excited level has an $\approx 4\times$ smaller coefficient than the
resonance line.  Therefore, the majority of photons absorbed at
$\lambda 2600$ are re-emitted with the same energy and only scatter 
in frequency space around the line.  For \feiia, the transitions to
the a~$^6$D$_{7/2}$ and a~$^6$D$_{5/2}$ levels have comparable and
even larger A coefficients than that to the ground-state.  Therefore,
the majority of photons absorbed at $\lambda 2586$ are re-emitted 
as longer wavelength \ion{Fe}{2}~$\lambda 2612$ or $\lambda 2632$
photons.  [Comment on total EW for 2586?]

@@

[Update the EW values with the new FeII data]

Our algorithm tracks the spatial emissivity of the source+wind
complex as a function of frequency.  Therefore, it is straightforward
to construct surface-brightness maps of the emission yielding a
dataset analagous to intergral-field-unit (IFU) observations.  In
Figure~\ref{fig:fig_fiducial_ifu_mgii}, we present the output for our
fiducial wind model at several velocities relative to the \mgiia\
transition. At $\mvr \le -200 \mkms$, where the wind has an optical
depth $\tau_{2796} < 1$ (Figure~\ref{fig:fig_fiducial_nvt}),
the source contributes significantly to the observed flux.  
At $\mvr=-100 \mkms$, however, the
wind absorbs all photons from the source and the observed emission is
entirely due to photons scattered by the wind.  This
emission significantly exceeds that for $\mvr = -200\mkms$ which
explains the fact that the absorption peaks at a velocity offset from
the peak in the wind's optical depth. [word] At $v_{\rm r} \ge 0
\mkms$,  both the source and wind contribute to the observed emission.

[Spatial cut?]

[FeII emission;  2600 and 2612]

@@

\begin{figure}
\epsscale{0.8}
\plotone{Figures/energy_levels.ps}
\caption{
Energy level diagrams for the \mgiid\ doublet and the UV1
multiplet of \ion{Fe}{2} transitions.   Each transition shown is
labelled by its rest wavelength (\AA) and Einstein A-coefficient
(s$^{-1}$). Black updward arrows
indicate the resonance-line transitions connected to the ground
state of each ion.  The 2p$^6$3p configuration of Mg$^+$ is split into
two energy levels that give rise to the \mgiid\ doublet.  
Both the 3d$^6$4s ground state and 3d$^6$4p upper level of Fe$^+$
are split into multiple energy levels giving rise to a series of
electric-dipole transitions between these fine-structure levels.   
The downward (green) arrows show the transitions connected to the
resonance-line transitions (i.e.\ they share the same upper energy
levels).  We also show a pair of levels (\ion{Fe}{2}~$\lambda\lambda
2618,2631$) that arise from even higher levels [Should we bother?]
Based on Figure~7 from \cite{hartagan9X}.
}
\label{fig:energy}
\end{figure}

@@

\begin{figure}
\epsscale{0.8}
\plotone{Figures/fig_fiducial_ifu_mgii.ps}
\caption{
Surface-brightness emission maps around the \mgiia\ transition for the
source+wind complex.  The middel panel shows the 1D spectrum with $v=0
\mkms$ corresponding to $\lambda = 2796.35$ and the dotted vertical
curves indicating the velocity slices for the emission maps.  The
source has a size $r_{\rm source} = 0.5$\,kpc, traced by a few
pixels at the center.   At $\mvr=-200 \mkms$, the wind has an optical
depth of $\tau_{2796} \approx 1$ such that the source contributes
significantly to the observed flux.  At $\mvr=-100 \mkms$, however, the
wind absorbs all photons from the source and the observed emission is
entirely due to photons scattered by the wind.  Surprisingly, this
emission exceeds that observed at $\mvr = -200\mkms$. At $\mvr \ge 0
\mkms$,  both the source and wind contribute to the observed emission.
}
\label{fig:fiducial_ifu_mgii}
\end{figure}

>>>>

\documentclass[12pt,preprint]{aastex}
\usepackage{natbib,amsmath}

\special{papersize=8.5in,11in}
\begin{document}

\newcommand{\maconfig}{2p$^6$3s}
\newcommand{\mbconfig}{2p$^6$3p}
\newcommand{\aconfig}{a~$^6$D$^0$}
\newcommand{\zconfig}{z~$^6$D$^0$}
\newcommand{\mvr}{v_{\rm r}}
\newcommand{\naid}{\ion{Na}{1}~$\lambda\lambda 5891, 5897$}
\newcommand{\mgiid}{\ion{Mg}{2}~$\lambda\lambda 2796, 2803$}
\newcommand{\mgiia}{\ion{Mg}{2}~$\lambda 2796$}
\newcommand{\mgiib}{\ion{Mg}{2}~$\lambda 2803$}
\newcommand{\feiia}{\ion{Fe}{2}~$\lambda 2586$}
\newcommand{\feiib}{\ion{Fe}{2}~$\lambda 2600$}
\newcommand{\feiid}{\ion{Fe}{2}~$\lambda\lambda 2586, 2600$}
\newcommand{\nmg}{$n_{\rm Mg^+}$}
\newcommand{\mnmg}{n_{\rm Mg^+}}
\newcommand{\nfe}{$n_{\rm Fe^+}$}
\newcommand{\mnfe}{n_{\rm Fe^+}}
\def\hub{h_{72}^{-1}}
\def\umfp{{\hub \, \rm Mpc}}
\def\mzq{z_q}
\def\zabs{$z_{\rm abs}$}
\def\mzabs{z_{\rm abs}}
\def\intl{\int\limits}
\def\cmma{\;\;\; ,}
\def\perd{\;\;\; .}
\def\ltk{\left [ \,}
\def\ltp{\left ( \,}
\def\ltb{\left \{ \,}
\def\rtk{\, \right  ] }
\def\rtp{\, \right  ) }
\def\rtb{\, \right \} }
\def\sci#1{{\; \times \; 10^{#1}}}
\def \rAA {\rm \AA}
\def \zem {$z_{\rm em}$}
\def \mzem {z_{\rm em}}
\def\smm{\sum\limits}
\def \cmm  {cm$^{-2}$}
\def \cmmm {cm$^{-3}$}
\def \kms  {km~s$^{-1}$}
\def \mkms  {{\rm km~s^{-1}}}
\def \lyaf {Ly$\alpha$ forest}
\def \Lya  {Ly$\alpha$}
\def \lya  {Ly$\alpha$}
\def \mlya  {Ly\alpha}
\def \Lyb  {Ly$\beta$}
\def \lyb  {Ly$\beta$}
\def \lyg  {Ly$\gamma$}
\def \ly5  {Ly-5}
\def \ly6  {Ly-6}
\def \ly7  {Ly-7}
\def \nhi  {$N_{\rm HI}$}
\def \mnhi  {N_{\rm HI}}
\def \lnhi {$\log N_{HI}$}
\def \mlnhi {\log N_{HI}}
\def \etal {\textit{et al.}}
\def \lyaf {Lyman--$\alpha$ forest}
\def \mnmin {\mnhi^{\rm min}}
\def \nmin {$\mnhi^{\rm min}$}
\def \O {${\mathcal O}(N,X)$}
\newcommand{\cm}[1]{\, {\rm cm^{#1}}}
\def \snrlim {SNR$_{lim}$}

@@

\begin{abstract}
\begin{itemize}
\item Emission is a generic feature of (nearly) isotropic winds.  This
  emission fills in absorption at $v \approx 0$, significantly
  complicating the absorption-line analysis. 
\end{itemize}
\end{abstract}

@@

The Mg$^+$ ion, with a single 3s electron in the ground-state,
exhibits an alkali doublet of transitions similar to the
\lya\ transitions of neutral hydrogen.  In Figure~\ref{fig:energy}
we present the energy level diagram for this 
\mgiid\ doublet.  In non-relativistic quantum
mechanics, the 2p$^6$3p level is said to be split by spin-orbit
coupling which produces the line doublet.  These are the only
\ion{Mg}{2} electric-dipole transitions 
with wavelengths near 2800\AA. Also, the transtion connecting
the $\rm {}^2P_{3/2}$ and $\rm {}^2P_{1/2}$ states is forbidden by several
selection rules.  Therefore, an absorption from
\maconfig~$\to$~\mbconfig\
is followed nearly 100$\%$ of the time by a spontaneous decay to the
ground state and our treatment will ignore any other possibilities
(e.g.\ absorption of a second photon).

@@

Iron exhibits the most complex set of energy levels of the elements
frequently studied in astrophysics.  The Fe$^+$ ion alone has over XXX
energy levels recorded \citep{iron}, and even this is an
incomplete list.  
One reason for the complexity of iron is
that the majority of its configurations exhibit fine-structure splitting.
This includes the ground-state configuration (\aconfig) which is split
into 5 levels with 
excitation energies $T_{\rm ex} \equiv \Delta E / k$ ranging from
$T_{\rm ex} \approx 500-1500$\,K.  These levels are usually labelled by the total angular momentum
$J$, with the ground-state having $J=9/2$ (Figure~\ref{fig:energy}).  
Transitions between these fine-structure levels are 
forbidden (magnetic-dipole) with spontaneous decay times of several hours.

@@

In Figure~\ref{fig:fiducial_nvt} we plot the density and velocity
profiles against radius for the fiducial wind model;  
their single power-law expressions are evident.  The figure also
shows the optical depth profile for the \mgiia\ transition ($\tau_{2796}$).
This profile is what determines the observed absorption/emission lines
for the wind.  
Although plotted against radius, we first calculated $\tau_{2796}$ 
as a function of velocity by summing the opacity in a series of
discrete and small radial intervals
between $r_{\rm inner}$  and $r_{\rm outer}$.   We then mapped
$\tau_{2796}$ onto radius using the radial velocity profile and 
checked that this profile is in good agreement with
the Sobolev approximation.  
The $\tau_{2796}$ profile peaks at $\tau_{2796}^{\rm max} \approx 30$
at a velocity $v \approx 65 \mkms$ corresponding to $r \approx 1.3
r_{\rm inner}$.  The optical depth profile for the \mgiib\ transition
is scaled down by the ratio of $f\lambda$ but otherwise identical.  Similarly,
the optical depth profiles for the \feiid\ transitions are
scaled down by $f \lambda$ and the \nfe/\nmg\ ratio.  
The adopted Doppler parameter
(here $b_{\rm turb} = 15 \mkms$) also has a modest impact on the results,
specially at large optical depths.  A larger/smaller
$b$-value would imply ... [FILL IN]
In turn, this would affect the resulting emission profiles.

Because the results are dictated by the $\tau_{2796}$ profile and the
Doppler parameter, the actual dimensions and density of the wind are
essentially unimportant provided they scale together to give the same
$\tau_{2796}$ profile.  Therefore, one may consider our choices for
$r_{\rm inner}, r_{\rm outer}, n_{\rm H}^0$ as arbitrary.
Nevertheless, we attempted to adopt values for this fiducial model
that some astrophysical motivation.

Using the methodology described in $\S$~\ref{sec:method}, we
propogated photons from the source and through the outflow to an
`observer' at $r \gg r_{\rm outer}$ that views the entire wind+source
complex.  Figure~\ref{fig:fiducial_1d} presents the spectrum
that this observer would record with the ``unattenuated'' source flux
normalized to unit value.   The \ion{Mg}{2} profiles
show the canonical `P-Cygni profile' that characterize a continuum
source embedded within an outflow.  Strong absorption is evident at
$v < -50 \mkms$ in both transitions and each shows emission at
positive velocities.  For this isotropic and dust-free model, the
total equivalent width of the doublet must be zero
(Table~\ref{tab:fiducial_EW}), i.e.\ every photon
absorbed still escapes the system, primarily at lower
energies.  The wind simply shuffles photons in frequency space.

Focusing on the \ion{Mg}{2} absorption, one notes the profiles have
positive intensity yet similar depth even though their $f\lambda$
values differ by a factor of two.  In standard absorption line
analysis, this is generally 
the tell-tale signature of a `cloud' that has a high optical depth (i.e.\
saturated) which only partially covers the emitting source
\citep[e.g.][]{hamman10}.  Our fiducial wind model, however, 
{\it entirely} covers the source; the apparent partial covering must
be related to a different effect.
Figure~\ref{fig:noemiss}, which compares the true
absorption profiles against the case where absorbed photons are not
re-emitted, further illustrates this issue.   As expected from the
$\tau_{2796}$ profile (Figure~\ref{fig:fiducial_nvt}, the no-emission
case predicts a strong \mgiid\ doublet that absorbs all photons at
$v \approx -100 \mkms$, i.e.\ $I_{2796} = \exp(-\tau_{2796}) \approx 0$.
The actual profile, meanwhile, has been `filled in' at $v \approx -100
\mkms$ by photons scattered and re-emitted by the wind (see below).  An
absorption-line analysis that ignores these effects
\citep[e.g.][]{sato} would systematically underestimate the true optical
depth and falsely conclude partial covering.  We will find that this
behaviour is a generic results for models with a high degree of
isotropy.
[Dan's analytic calculation here? or Appendix?]

One also notes that the emission profiles of the \mgiid\ doublet
are very similar and have comparable equivalent widths.  In fact the
flux of the \mgiib\ transition even exceeds that for \mgiia.  The
emission profiles are similar because the absorption is saturated.
Furthermore, the flux from \mgiib\ is greater than that for
\mgiia\ because the wind speed exceeds the velocity separation
of the doublet, $|\mvr|_{\rm max} > (\Delta v)_{\rm MgII}$, such
that the \mgiib\ absorption profile partially absorbs the red wing of the
\mgiia\ emission profile.  The relative strengths of the emission
lines, therefore, is sensitive to both the optical depth and velocity
extent of the wind.

Now consider the \ion{Fe}{2} transitions.
The bottom left panel of Figure~\ref{fig:fiducial_1d} covers the
majority of the \ion{Fe}{2} UV1 transitions and several are
shown in the velocity plot.  The line
profile for \feiib\ is very similar to those for the \mgiid\ doublet;
one observes strong absorption to negative velocities and strong
emission at $v > 0 \mkms$ producing a P-Cygni profile.  Splitting
the profile at $v = -50 \mkms$, we measure an equivalent width
$W_{2600}^{\rm abs} = 1.16$\AA\ in absorption and $W_{2600}^{\rm em} =
-0.94$\AA\ in emission (Table~\ref{tab:fiducial_EW}) for a total
equivalent width of $W_{2600}^{\rm TOT} \approx 0.22$\AA.  
[Point out that if $\tau_{2600}$ were higher, than the photons would
likely be more trapped and more would come out as 2626.  Also a
v=0km/s component might make quite a difference.]
In contrast, the \feiia\ resonance line shows much weaker emission and
a much higher total equivalent width ($W_{2586}^{\rm TOT} = 0.49$\AA)
even though the line has a $2 \times$ lower $f\lambda$ value.
The difference comes the extra downward transition from the
\zconfig$_{7/2}$ level and (more importantly) that the Einstein A
coefficients  of the non-resonant lines match and even exceed that for
the resonant line.  In the case of \feiib, the
\ion{Fe}{2}~2626 transition 
has an approximately  $4\times$ smaller coefficient than the
resonance line.  Therefore, the majority of photons absorbed at
$\lambda 2600$ are re-emitted with the same energy and only scatter 
in frequency space around the line.  For \feiia, 
the majority of photons absorbed are re-emitted 
as longer wavelength \ion{Fe}{2}~$\lambda 2612$ or $\lambda 2632$
photons.  
The total equivalent width, however, of the lines connected to the
\zconfig$_{7/2}$ upper level does vainsh (i.e.\ photons are conserved
in this fiducial wind).

@@

Our 3D Monte Carlo algorithm tracks the spatial emissivity of the source+wind
complex as a function of frequency.  From this output, we
constructed surface-brightness maps producing a
dataset analagous to intergral-field-unit (IFU) observations.  In
Figure~\ref{fig:fiducial_ifu_mgii}, we present the output for our
fiducial wind model at several velocities relative to the \mgiia\
transition. At $\mvr \le -200 \mkms$, where the wind has an optical
depth $\tau_{2796} < 1$ (Figure~\ref{fig:fig_fiducial_nvt}),
the source contributes significantly to the observed flux.  
At $\mvr=-100 \mkms$, however, the
wind absorbs all photons from the source and the observed emission is
entirely from photons scattered by the wind.  This scattered emission
actually exceeds the source+wind emission at 
$\mvr = -200\mkms$ such
that the absorption profile reaches peak depth at a velocity that is
negatively offset from
the peak in optical depth.  The net result of the scattered photons is
a weaker \ion{Mg}{2} profile that is offset fromt he true optical
depth profile.  Clearly, this will complicate efforts to estimate the
speed, covering fraction, and total column density of the wind.  At $v
= 0 \, \mkms$, the wind and source have comparable total flux and the
latter dominates at higher velocities.  
At $v_{\rm r} \ge 0
\mkms$,  both the source and wind contribute to the observed emission.

[Spatial cut? Yes]

Similar characteristics are observed for the \ion{Fe}{2} resonance
transitions (Figure~\ref{fig:fiducial_ifu_feii2600}).
For transitions to fine-structure levels of the \aconfig, the source
is unattenuated but there is also a significant contribution from the
wind (Figure~\ref{fig:fiducial_ifu_feii2612}).
[Show a cut and comment on the fraction of light in 1-3\,kpc, 1-10,
and 1-20; ignoring the source]

@@

\begin{figure}
\epsscale{0.8}
\plotone{Figures/energy_levels.ps}
\caption{
Energy level diagrams for the \mgiid\ doublet and the UV1
multiplet of \ion{Fe}{2} transitions   
(based on Figure~7 from \cite{hmt+99}).
Each transition shown is
labelled by its rest wavelength (\AA) and Einstein A-coefficient
(s$^{-1}$). Black updward arrows
indicate the resonance-line transitions connected to the ground
state of each ion.  The 2p$^6$3p configuration of Mg$^+$ is split into
two energy levels that give rise to the \mgiid\ doublet.  
Both the 3d$^6$4s ground state and 3d$^6$4p upper level of Fe$^+$
exhibit fine-structure splitting that gives rise to a series of
electric-dipole transitions. 
The downward (green) arrows show the transitions connected to the
resonance-line transitions (i.e.\ they share the same upper energy
levels).  We also show a pair of levels (\ion{Fe}{2}~$\lambda\lambda
2618,2631$) that arise from higher levels in the \zconfig\
configuration.  These transitions have not yet been observed in
galactic-scale outflows and are not considerd in our analysis.
}
\label{fig:energy}
\end{figure}

@@

\begin{figure}
\epsscale{0.8}
\plotone{Figures/fig_fiducial_ifu_mgii.ps}
\caption{
Surface-brightness emission maps around the \mgiia\ transition for the
source+wind complex.  The middel panel shows the 1D spectrum with $v=0
\mkms$ corresponding to $\lambda = 2796.35$\AA\ and the dotted vertical
curves indicating the velocity slices for the emission maps.  The
source has a size $r_{\rm source} = 0.5$\,kpc, traced by a few
pixels at the center.   At $\mvr=-200 \mkms$, the wind has an optical
depth of $\tau_{2796} \approx 1$ such that the source contributes
significantly to the observed flux.  At $\mvr=-100 \mkms$, however, the
wind absorbs all photons from the source and the observed emission is
entirely due to photons scattered by the wind.  Surprisingly, this
emission exceeds that observed at $\mvr = -200\mkms$. At $\mvr \ge 0
\mkms$,  both the source and wind contribute to the observed emission.
}
\label{fig:fiducial_ifu_mgii}
\end{figure}

\begin{figure}
\epsscale{0.8}
\plotone{Figures/fig_fiducial_ifu_feii2600.ps}
\caption{
Surface-brightness emission maps around the \feiib\ transition for the
source+wind complex.  The middle panel shows the 1D spectrum with $v=0
\mkms$ corresponding to $\lambda = 2600.173$\AA\ and the dotted vertical
curves indicating the velocity slices for the emission maps.  
The results are very similar to those observed for the \mgiid\ doublet
(Figure~\ref{fig:fiducial_ifu_mgii}).
}
\label{fig:fiducial_ifu_feii2600}
\end{figure}

\begin{figure}
\epsscale{0.8}
\plotone{Figures/fig_fiducial_ifu_feii2612.ps}
\caption{
Surface-brightness emission maps around the \ion{Fe}{2}~$\lambda 2612$ transition for the
source+wind complex.  The middle panel shows the 1D spectrum with $v=0
\mkms$ corresponding to $\lambda = 2612.654$\AA\ and the dotted vertical
curves indicating the velocity slices for the emission maps.  
In this case, the source is unattenuated yet scattered photons from
the wind also have a significant contribution. 
}
\label{fig:fiducial_ifu_feii2612}
\end{figure}
